---
output: 
  html_document:
    includes:
      in_header: test1.html
runtime: shiny_prerendered
description: "practice app 2"
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
knitr::opts_chunk$set(echo = FALSE)
tutorial_options(exercise.eval = FALSE)
knitr::opts_chunk$set(exercise.checker = gradethis::grade_learnr)
library(palmerpenguins)
library(broom)
library(knitr)

```

```{css, echo=FALSE}
p {
  font-size: 16.5px;
  font-family: "Merriweather", sans-serif;
}

h5 {
  font-size: 16.5px;
  font-family: "Lato", sans-serif;
}

```

```{r prepare, warning=FALSE, message=FALSE}
mod1 <- lm(body_mass_g ~ bill_length_mm, data = penguins)
```

How do we change the summary output from a long list into a data.frame? call it `mod1.pretty`.

```{r ex1, exercise = TRUE, exercise.setup = "prepare"}

```

<div id="ex1-hint">

<font size="-1.5">
Use the tidyverse version
</font>
</div>


```{r ex1-solution}
mod1.pretty <- tidy(mod1)
kable(mod1.pretty)
```

```{r ex1-check}
grade_code()
```

How do we make a data.frame that has important information like predicted values, outlier metrics etc.?

Be sure to store it as an object called `mod1.predicted` and use the `kable` function to make it a pretty output. Also, only show the first few rows. 

```{r ex2, exercise = TRUE, exercise.setup = "prepare"}

```

<div id="ex2-hint">

<font size="-1.5">
Use the tidyverse version
</font>
</div>


```{r ex2-solution}
mod1.predicted <- augment(mod1)
kable(head(mod1.predicted))
```

```{r ex2-check}
grade_code()
```

How do we make a data.frame that has fit statistics?

Be sure to store it as an object called `mod1.fit` and use the `kable` function to make it a pretty output.

```{r ex3, exercise = TRUE, exercise.setup = "prepare"}

```

<div id="ex3-hint">

<font size="-1.5">
Use the tidyverse version
</font>
</div>


```{r ex3-solution}
mod1.fit <- glance(mod1)
kable(mod1.fit)
```

```{r ex3-check}
grade_code()
```
<div data-iframe-height></div>