---
output: 
  html_document:
    includes:
      in_header: test1.html
runtime: shiny_prerendered
description: "Vectors & Classes"
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
knitr::opts_chunk$set(echo = FALSE)
tutorial_options(exercise.eval = FALSE)
knitr::opts_chunk$set(exercise.checker = gradethis::grade_learnr)

```

```{css, echo=FALSE}
p {
  font-size: 18px;
  font-family: "Merriweather"; sans-serif;
}

h5 {
  font-size: 16.5px;
  font-family: "Lato";
  font-weight: 700
}


```

##### 1. Make the vectors

```{r vecs, exercise = TRUE}

```

<div id="vecs-hint">
<font size="-1.5">
**Hint 1:** You do *not* need to print out the objects. Simply make the vectors (If you get that weird "invisible" warning, you can ignore it).

**Hint 2:** Spelling, commas, quotations, and parentheses constitute ~80% of all errors in programming!
</font>
</div>

```{r vecs-solution}
ids <- c("ID1", "ID2", "ID3", "ID4", "ID5")
state <- c("Missouri", "Iowa", "Missouri", "Idaho", "Maine")
smoker <- c(TRUE, FALSE, FALSE, TRUE, FALSE)
age <- c(20, 18, 32, 25, 25)

```

```{r vecs-check}
grade_code()
```

##### 2. Check the class of each vector

```{r prepare-vecs}
ids <- c("ID1", "ID2", "ID3", "ID4", "ID5")
state <- c("Missouri", "Iowa", "Missouri", "Idaho", "Maine")
smoker <- c(TRUE, FALSE, FALSE, TRUE, FALSE)
age <- c(20, 18, 32, 25, 25)

```

```{r classes, exercise = TRUE, exercise.setup = "prepare-vecs"}

```

<div id="classes-hint">
<font size="-1.5">
**Hint:** Check out the "Object Classes" tab from the "2: Objects" slides if you don't know how to check and object's class
</font>
</div>

```{r classes-solution}
class(ids)
class(state)
class(smoker)
class(age)

```

```{r classes-check}
grade_code()
```

Our code is correct, but maybe we want `state` to actually be a **factor**. Factors are a special type of character variables that represent categories. To make `state` into a factor, run the following line of code. *Keeping this line of code*, now add a new line to re-check it's class. 

```{r fac, exercise = TRUE, exercise.setup = "prepare-vecs"}
state <- factor(state)
```

<div id="fac-hint">
<font size="-1.5">
**Hint:** Revisit the previous exercise if you're unsure how to check the class.
</font>
</div>

```{r fac-solution}
state <- factor(state)

class(state)

```

```{r fac-check}
grade_code()
```
