---
output: 
  html_document:
    includes:
      in_header: test1.html
runtime: shiny_prerendered
description: "Objects part 1"
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
knitr::opts_chunk$set(echo = FALSE)
tutorial_options(exercise.eval = FALSE)
knitr::opts_chunk$set(exercise.checker = gradethis::grade_learnr)
```

```{r continents, exercise=TRUE, warning=FALSE, message=FALSE}

```

<div id="continents-hint">
**Hint 1:** The object you want to store should be on the right hand side of the `<-` and the name you want to give your new object should be on the left hand side of the `<-`. Similar to a mathematical equation!

**Hint 2:** At this point, nothing should print out (except whether you got the answer correct or incorrect)
</div>

```{r continents-solution}
continents <- 7
```

```{r continents-check}
grade_code("Good job!")
```

##### Things to note:
1. If you were to run this line of code from within RStudio, you would see the word `continents` in the Environment pane (upper right side). This is an easy way for you to glance over and see if your object is actually stored. 

2. Notice that nothing printed out when you ran the code above. That code simply says *"store the number `7` in an object called `continents`"*. No where does it say *"show me what is stored in the `continents` object*. To do that, you simply need to type it out again, like this:

```{r, echo=TRUE}
continents <- 7
continents
```

`r emo::ji("index_pointing_up")` Now you can see that `7` is stored in the object `continents`.

In your research, most of the time, you don't necessarily want to print out every object. But it's very helpful for things like homework assignments or showing your collaborators an answer/value. 

#### Quick Q:

```{r script-console, echo=FALSE}
question("Now that you have made your `continents` object, what is the difference between typing `continents` in the console vs. in a script file?",
         answer("If it's in the console, once you hit 'Enter', the number '7' should immediately print out. If it's in the script, once you hit 'Enter' your cursor will go to the next line, but 7 will not print out until you hit 'Run'", correct = TRUE),
         answer("If it's in the console, once you hit 'Enter' your cursor will go to the next line, but '7' will not print out until you hit 'Run'. If it's in the script, once you hit 'Enter', the number '7' should immediately print out",
                message = "Remember, the console is more like your instant messenger and the script is more like an email draft!"),
         allow_retry = TRUE)
```

#### The whole point of making an object is that you can do things with them!

For example:
```{r, echo=TRUE}
# I have 5 chickens
chickens <- 5

# I have 4 cows
cows <- 4

# How many animals do I have in total?
chickens + cows
```

You can also update your objects!

```{r, echo=TRUE}
# I sold 3 chickens
chickens <- chickens - 3

# I bought 4 cows
cows <- cows + 4

# What is my new total number of animals?
# Still the same line of code from before!
chickens + cows
```

In this scenario, we did an "overwrite" of our original `chickens` and `cows` objects. We could have stored those as new objects. Something like: `chickens_new <- chickens - 3`. You will need to decide whether it makes sense to overwrite an object or to create a new one. Base it on what you're trying to accomplish. 

#### Quick Q:
```{r store, echo=FALSE}
question("Where is the answer of `chickens + cows` stored?",
         answer("No where", correct = TRUE),
         answer("Global Environment",
                message = "HINT: What is the name of the object that should house this answer?"),
         answer("Console",
                message = "The console prints things out and tells you what you've done. Things aren't necessarily 'stored' there, though"),
         answer("Script",
                message = "The script is like an email draft. It will send if you hit 'Run'. But things aren't necessarily 'stored' there -- they are created there!"),
         random_answer_order = TRUE,
         allow_retry = TRUE)
```

<div data-iframe-height></div>