---
output: 
  html_document:
    includes:
      in_header: test1.html
runtime: shiny_prerendered
description: "anova setup"
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
knitr::opts_chunk$set(echo = FALSE)
tutorial_options(exercise.eval = FALSE)
knitr::opts_chunk$set(exercise.checker = gradethis::grade_learnr)

```

```{css, echo=FALSE}
p {
  font-size: 16.5px;
  font-family: "Merriweather", sans-serif;
}

h5 {
  font-size: 16.5px;
  font-family: "Lato", sans-serif;
}

```

```{r prepare, warning=FALSE, message=FALSE}

# need to read in files "by hand"

list_of_dataframes <- list(
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject1.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject2.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject3.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject4.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject5.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject6.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject7.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject8.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject9.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject10.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject11.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject12.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject13.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject14.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject15.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject16.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject17.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject18.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject19.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject20.csv")
) # initialize


```

Drew has 20 different spreadsheets from her research project, one per subject. All of the spreadsheets are the same format. Drew has already loaded all of the spreadsheets in R, and saved them to a list called `list_of_dataframes`. Each subject's spreadsheet can be indexed like so `list_of_dataframes[[1]]` which produces this output:

```{r prep1, warning=FALSE, message=FALSE}

list_of_dataframes <- list(
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject1.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject2.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject3.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject4.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject5.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject6.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject7.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject8.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject9.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject10.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject11.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject12.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject13.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject14.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject15.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject16.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject17.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject18.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject19.csv"),
  read.csv("https://relaxed-swirles-04c8f0.netlify.app/practice/20-practice_files/data/subject20.csv")
) # initialize

list_of_dataframes[[1]]
```

**How can Drew use a for loop to combine these files into one large dataframe?**

Key things to keep in mind:

- There are 20 subjects. Each subject can be indexed like Subjects 1 (example above)
- The columns of all the dataframes are exactly the same
- HINT: Look at the help page for `rbind()`


```{r ex1, exercise = TRUE, exercise.setup = "prepare"}
# Replace instances of `XXX` in the skeleton code below and then check your # result.

# For each individual data.frame, call it `i_dataframe`.
# For the final combined data.frame, call it `combined_dataframe`. 

XXX <- NULL

for (i in 1:20) {
  XXX <- list_of_dataframes[[XXX]]
  combined_dataframe <- rbind(XXX, XXX)
}

# Print it out so we can see!
combined_dataframe
```

<div id="ex1-hint">

<font size="-1.5">
The goal is to get each individual data.frame and rather than keep it as a separate thing, you want the output to be a single large data.frame, where each individual is appended underneath the next. 
</font>
</div>


```{r ex1-solution}
combined_dataframe <- NULL

for (i in 1:20) {
  i_dataframe <- list_of_dataframes[[i]]
  combined_dataframe <- rbind(combined_dataframe, i_dataframe)
}

combined_dataframe <- combined_dataframe %>% 
  arrange(subject)
combined_dataframe
```

```{r ex1-check}
grade_code()
```

<div data-iframe-height></div>