---
output: 
  html_document:
    includes:
      in_header: test1.html
runtime: shiny_prerendered
description: "anova setup"
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
knitr::opts_chunk$set(echo = FALSE)
tutorial_options(exercise.eval = FALSE)
knitr::opts_chunk$set(exercise.checker = gradethis::grade_learnr)

```

```{css, echo=FALSE}
p {
  font-size: 16.5px;
  font-family: "Merriweather", sans-serif;
}

h5 {
  font-size: 16.5px;
  font-family: "Lato", sans-serif;
}

```

```{r prepare, warning=FALSE, message=FALSE}
library(tidyverse)
names_of_dataframes <- dir(path = "/Users/Coop/Psych4175/content/practice/Practice_Data/", full.names = TRUE, pattern = '.csv', ignore.case = TRUE)

list_of_dataframes <- list() # initialize

for (i in 1:length(names_of_dataframes)) {
  list_of_dataframes[[i]] <- read.csv(names_of_dataframes[i], header = TRUE)
}

```

Drew has 20 different spreadsheets from her research project, one per subject. All of the spreadsheets are the same format, and look like this:

```{r prep1, warning=FALSE, message=FALSE}
names_of_dataframes <- dir(path = "/Users/Coop/Psych4175/content/practice/Practice_Data/", full.names = TRUE, pattern = '.csv', ignore.case = TRUE)

list_of_dataframes <- list() # initialize

for (i in 1:length(names_of_dataframes)) {
  list_of_dataframes[[i]] <- read.csv(names_of_dataframes[i], header = TRUE)
}

head(list_of_dataframes[[1]])
```

Drew has already loaded all of the spreadsheets in R, and saved them to a list called `list_of_dataframes`. Each subject's spreadsheet can be indexed like so `list_of_dataframes[[1]]` which produces this output:

```{r prep2, warning=FALSE, message=FALSE}
names_of_dataframes <- dir(path = "../Practice_Data/", full.names = TRUE, pattern = '.csv', ignore.case = TRUE)

list_of_dataframes <- list() # initialize

for (i in 1:length(names_of_dataframes)) {
  list_of_dataframes[[i]] <- read.csv(names_of_dataframes[i], header = TRUE)
}

# Indexing Subject 1's dataframe:
list_of_dataframes[[1]]
```

**How can Drew use a for loop to combine these files into one large dataframe?**

Key things to keep in mind:

- There are 20 subjects. Each subject can be indexed like Subjects 1 (example above)
- The columns of all the dataframes are exactly the same
- HINT: Look at the help page for `rbind()`


```{r ex1, exercise = TRUE, exercise.setup = "prepare"}
# Replace instances of `XXX` in the skeleton code below and then check your # result.

# For each individual data.frame, call it `i_dataframe`.
# For the final combined data.frame, call it `combined_dataframe`. 

XXX <- NULL

for (i in 1:20) {
  XXX <- list_of_dataframes[[XXX]]
  combined_dataframe <- rbind(XXX, XXX)
}

# After you do this, we're going to arrange this by subject number
# Then, print it out so we can see. You do NOT need to modify this code
combined_dataframe <- combined_dataframe %>% 
  arrange(subject)
combined_dataframe
```

<div id="ex1-hint">

<font size="-1.5">
The goal is to get each individual data.frame and rather than keep it as a separate thing, you want the output to be a single large data.frame, where each individual is appended underneath the next. 
</font>
</div>


```{r ex1-solution}
combined_dataframe <- NULL

for (i in 1:20) {
  i_dataframe <- list_of_dataframes[[i]]
  combined_dataframe <- rbind(combined_dataframe, i_dataframe)
}

combined_dataframe <- combined_dataframe %>% 
  arrange(subject)
combined_dataframe
```

```{r ex1-check}
grade_code()
```

<div data-iframe-height></div>