---
output: 
  html_document:
    includes:
      in_header: test1.html
runtime: shiny_prerendered
description: "Indexing"
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
knitr::opts_chunk$set(echo = FALSE)
tutorial_options(exercise.eval = FALSE)
knitr::opts_chunk$set(exercise.checker = gradethis::grade_learnr)

```

```{css, echo=FALSE}
p {
  font-size: 16.5px;
  font-family: "Merriweather", sans-serif;
}

h5 {
  font-size: 16.5px;
  font-family: "Lato", sans-serif;
}

```

```{r prepare-sat, warning=FALSE, message=FALSE}
library(psych)
sat.act <- sat.act[1:100,]
age <- sat.act$age
act <- sat.act$ACT
satV <- sat.act$SATV
satQ <- sat.act$SATQ
rm(sat.act)

satTotal <- satV + satQ
scaledSat <- satTotal * .0225
avgTestScores <- (scaledSat + act) / 2
```

##### 1. Get the first five `satQ` scores, the first five `satV` scores, and the first five `satTotal` scores. Does `satQ + satV = satTotal`?
This kind of code is great for checking your work! For example, if you find that `satQ + satV` DOES NOT equal `satTotal`, then you would know something is wrong with your code. 

```{r ex1, exercise = TRUE, exercise.setup = "prepare-sat"}

```

<div id="ex1-hint">
<font size="-1.5">
**Hint:** Your answer should have 3 lines of code. Spaces between the lines (empty lines) don't matter.
</font>
</div>

```{r ex1-solution}
satQ[1:5]

satV[1:5]

satTotal[1:5]
```

```{r ex1-check}
grade_code()
```

##### 2. Get the average test scores for the 43rd through 77th individual.

```{r ex2, exercise = TRUE, exercise.setup = "prepare-sat"}

```

<div id="ex2-hint">
<font size="-1.5">
**Hint:** You've already created this variable! Look to the section above to find the correct name.
</font>
</div>

```{r ex2-solution}
avgTestScores[43:77]
```

```{r ex2-check}
grade_code()
```

##### 3. Get the ages (`age`) for the following people:
1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 37, 38, 39, 40, 41, 42, 43, 44, 45, 66, 77, and 99. **DO NOT TYPE EVERY NUMBER BY HAND**. 

```{r ex3, exercise = TRUE, exercise.setup = "prepare-sat"}

```

<div id="ex3-hint">
<font size="-1.5">
**Hint:** You can combine things into a vector using `c()`. 
</font>
</div>

```{r ex3-solution}
age[c(1:16, 37:45, 66, 77, 99)]
```

```{r ex3-check}
grade_code()
```

<div data-iframe-height></div>
