---
output: 
  html_document:
    includes:
      in_header: test1.html
runtime: shiny_prerendered
description: "sequences"
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
knitr::opts_chunk$set(echo = FALSE)
tutorial_options(exercise.eval = FALSE)
knitr::opts_chunk$set(exercise.checker = gradethis::grade_learnr)

```

```{css, echo=FALSE}
p {
  font-size: 16.5px;
  font-family: "Merriweather", sans-serif;
}

h5 {
  font-size: 16.5px;
  font-family: "Lato", sans-serif;
}

```

Before we begin, let's remember our `empire` data.frame
```{r, echo=FALSE, warning = FALSE, message = FALSE}
library(dplyr)
library(knitr)
empire <- starwars

empire <- empire[c(1:5, 10, 13, 14, 19, 21), c(1:3, 8, 10, 11)]
empire$species <- factor(empire$species)

kable(empire)
```

```{r, prepare-empire, warning = FALSE, message = FALSE}
library(dplyr)
library(knitr)
empire <- starwars

empire <- empire[c(1:5, 10, 13, 14, 19, 21), c(1:3, 8, 10, 11)]
empire$species <- factor(empire$species)

```

##### 1. Look up the help documentation for the `scale` and `plot` functions
*Use `base::plot` to make sure that the correct help documentation shows up*. But you still need to add something to the beginning of `base::plot` to make the help page appear...
```{r q1, exercise=TRUE}

```

##### 2. Using the `height` variable from our `empire` data.frame, make a new variable called `height_z`, using the `scale` function.
Make this a separate vector -- do NOT append it to the existing `empire` data.frame. Go ahead and print it out. 
```{r, q2, exercise=TRUE, exercise.setup="prepare-empire"}

```

<div id="q2-hint">
<font size="-1.5">
**Hint:** We're naming it `height_z` because we're making z-scores!
</font>
</div>

```{r q2-solution}
height_z <- scale(empire$height)
height_z
```

```{r q2-check}
grade_code()
```

##### 3. Do the same thing for the `mass` variable, and call your new object `mass_z`. 
Make this a separate vector -- do NOT append it to the existing `empire` data.frame. Go ahead and print it out. 
```{r, q3, exercise=TRUE, exercise.setup="prepare-empire"}

```

<div id="q3-hint">
<font size="-1.5">
**Hint:** We're naming it `mass_z` because we're making z-scores!
</font>
</div>

```{r q3-solution}
mass_z <- scale(empire$mass)
mass_z
```

```{r q3-check}
grade_code()
```


```{r prepare-empire2, warning = FALSE, message = FALSE}
library(dplyr)
library(knitr)
empire <- starwars

empire <- empire[c(1:5, 10, 13, 14, 19, 21), c(1:3, 8, 10, 11)]
empire$species <- factor(empire$species)

height_z <- scale(empire$height)
mass_z <- scale(empire$mass)
```

##### 4. Make a new `data.frame` that only contains the `height_z` vector and the `mass_z` vector.
Store this new data.frame as `empire_z`. Print it out.
```{r q4, exercise=TRUE, exercise.setup="prepare-empire2"}

```

<div id="q4-hint">
<font size="-1.5">
**Hint:** Do *not* use the `cbind()` function. Use only functions that are highighted in this particular question.
</font>
</div>

```{r q4-solution, exercise.setup="prepare-empire2"}
empire_z <- data.frame(height_z, mass_z)
empire_z
```

```{r q4-check}
grade_code()
```

```{r prepare-empire3, warning = FALSE, message = FALSE}
library(dplyr)
library(knitr)
empire <- starwars

empire <- empire[c(1:5, 10, 13, 14, 19, 21), c(1:3, 8, 10, 11)]
empire$species <- factor(empire$species)

height_z <- scale(empire$height)
mass_z <- scale(empire$mass)

empire_z <- data.frame(height_z, mass_z)
```

##### 5. Make a scatter plot of standardized height (x-axis) by standardized mass (y-axis), using the `plot` function.
Add the following to your plot:

  - Make "Height by Mass" the **title** of the plot
  - Add a **label** to the **x-axis** that says "Height (z-scores)"
  - Add a **label** to the **y-axis** that says "Mass (z-scores)"

```{r q5, exercise=TRUE, exercise.setup="prepare-empire3"}

```

<div id="q5-hint">
<font size="-1.5">
**Hint 1:** Scroll up to the first part of this question and re-read the help documentation for `plot`

**_Bonus:_** If you're feeling good, try changing `type = "l` to your plot. What happens? Note: if you submit this code it will be graded as incorrect. But go ahead and play around with it (you can resubmit the correct code afterward).
</font>
</div>

```{r q5-solution, exercise.setup="prepare-empire3"}
plot(x = empire_z$height_z, y = empire_z$mass_z, 
     main = "Height by Mass",
     xlab = "Height (z-scores)",
     ylab = "Mass (z-scores)")
```

```{r q5-check}
grade_code()
```

##### 6. Put it all together in a single code chunk so you can see what you did!
Starting from question 2, re-type or simply copy/paste your code from above. The goal is to see everyting at once. 

The only exception is this time, do not print anything out (for example, after making `empire_z`, you don't need to type it out again to view it). You also don't need to re-print out the help documentation, which is why you can start at step 2. 

```{r q6, exercise=TRUE, exercise.setup="prepare-empire3"}

```
<div id="q6-hint">
<font size="-1.5">
**Hint:** You should have 3 lines of code before you get to the `plot` function.
</font>
</div>

```{r q6-solution, exercise.setup="prepare-empire3"}
height_z <- scale(empire$height)
mass_z <- scale(empire$mass)
empire_z <- data.frame(height_z, mass_z)

plot(x = empire_z$height_z, y = empire_z$mass_z, 
     main = "Height by Mass",
     xlab = "Height (z-scores)",
     ylab = "Mass (z-scores)")

```

```{r q6-check}
grade_code()
```

<div data-iframe-height></div>