---
output: 
  html_document:
    includes:
      in_header: test1.html
runtime: shiny_prerendered
description: "practice app 2"
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
knitr::opts_chunk$set(echo = FALSE)
tutorial_options(exercise.eval = FALSE)
knitr::opts_chunk$set(exercise.checker = gradethis::grade_learnr)

```

```{css, echo=FALSE}
p {
  font-size: 16.5px;
  font-family: "Merriweather", sans-serif;
}

h5 {
  font-size: 16.5px;
  font-family: "Lato", sans-serif;
}

```

```{r prepare, warning=FALSE, message=FALSE}

iris = iris

z_score = function(values){
  return((values-mean(values)) / sd(values))
}


```

```{r ex1, exercise = TRUE, exercise.setup = "prepare"}
# I'm going to help you initialize an empty data.frame
# This first line creates `iris_zscored`. it is a dataframe filled with
# NA values, and has the exact same dimensions as iris (same rows and cols)
# Do not change this code!

iris_zscored <- data.frame(matrix(NA, nrow = nrow(iris), ncol = ncol(iris)))

# Write your for loop here:



# Last, I'm going to assign the names of the columns of our new dataframe to be
# the same as the original. Do not change this code!

colnames(iris_zscored) <- colnames(iris)

# View the new z-scored data frame and 
# check out a summary of it dataset -- is the data z-scored?  
# Do not change the code below
head(iris_zscored)
summary(iris_zscored)


```

<div id="ex1-hint">

<font size="-1.5">
Hint 1: You are writing a for loop -- NOT a function! You're simply using the `z_score` function that you created inside of your for loop. So no return statement is necessary!
</font>

<font size="-1.5">
Hint 2: If `nrow()` tells you the number of rows, how do you think you get the number of columns? 
</font>

<font size="-1.5">
Hint 3: Think back to how we indexed things! When you have a 1-d object, it was something like `object[8]` to get the 8th element in the `object`. When it's a 2-d object, you need to specify rows and column. `object[6,4]` gives you the 6th row and the 4th column. If you want all of the rows or columns, you leave it blank. `object[7,]` gives you the 7th row and all of the columns.
</font>

</div>

```{r ex1-solution, warning = FALSE, message = FALSE}
# I'm going to help you initialize an empty data.frame
# This first line creates `iris_zscored`. it is a dataframe filled with
# NA values, and has the exact same dimensions as iris (same rows and cols)
# Do not change this code!

iris_zscored <- data.frame(matrix(NA, nrow = nrow(iris), ncol = ncol(iris)))

# Write your for loop here:

for(i in 1:ncol(iris)){
  
  if(is.numeric(iris[,i]) == TRUE) {
    z = z_score(values = iris[,i])
    iris_zscored[,i] <- z
  }
  
  else{
    iris_zscored[,i] <- iris[,i]
  }
}

# Last, I'm going to assign the names of the columns of our new dataframe to be
# the same as the original. Do not change this code!

colnames(iris_zscored) <- colnames(iris)

# View the new z-scored data frame and 
# check out a summary of it dataset -- is the data z-scored?  
# Do not change the code below
head(iris_zscored)
summary(iris_zscored)
```

```{r ex1-check}
grade_code()
```

<div data-iframe-height></div>