---
output: 
  html_document:
    includes:
      in_header: test1.html
runtime: shiny_prerendered
description: "Vectors & Indexing"
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
knitr::opts_chunk$set(echo = FALSE)
tutorial_options(exercise.eval = FALSE)
knitr::opts_chunk$set(exercise.checker = gradethis::grade_learnr)

```

```{css, echo=FALSE}
p {
  font-size: 16.5px;
  font-family: "Merriweather", sans-serif;
}

h5 {
  font-size: 16.5px;
  font-family: "Lato", sans-serif;
}

```

```{r prepare-empire, warning=FALSE, message=FALSE}
library(dplyr)
empire <- starwars

empire <- empire[c(1:5, 10, 13, 14, 19, 21), c(1:3, 8, 10, 11)]
empire$species <- factor(empire$species)
```

##### 1. Unit Conversions
Currently, the `height` variable in the `empire` data.frame is measured in centimeters. Make a new variable called `height_mm` that converts all the values into millimeters.

Let's add `height_mm` to the existing `empire` dataset. To do this, I have given you the LEFT side of the assignment (aka what to call the new variable). You need to fill in the RIGHT side of it. 

After doing so, print out the entire `empire` dataframe to see if your new variable is now included.

```{r ex1, exercise = TRUE, exercise.setup = "prepare-empire"}
empire$height_mm <- 
```

<div id="ex1-hint">
<font size="-1.5">
**Hint 1:** 1 centimeters = 10 millimeters
**Hint 2:** If you forgot how to do this, revisit some of the exercises with vectors.
</font>
</div>

```{r ex1-solution, exercise.setup = "prepare-empire"}
empire$height_mm <- empire$height * 10
empire
```

```{r ex1-check}
grade_code()
```

##### 2. Mini Data.frame
Make a new, mini data.frame called `empire_mini`. Only include the first 3 rows of `empire`, as well as the `mass` and `height_mm` columns. When doing this, **_ONLY USE INDEXING._** Do **NOT** use `data.frame()`. Print it out afterward.

```{r prepare-empire2, warning=FALSE, message=FALSE}
library(dplyr)
empire <- starwars

empire <- empire[c(1:5, 10, 13, 14, 19, 21), c(1:3, 8, 10, 11)]
empire$species <- factor(empire$species)

empire$height_mm <- empire$height * 10
```


```{r ex2, exercise = TRUE, exercise.setup = "prepare-empire2"}


```

<div id="ex2-hint">
<font size="-1.5">
**Hint: What positions are the columns in?** 
</font>
</div>

```{r ex2-solution, exercise.setup = "prepare-empire2"}
empire_mini <- empire[1:3, c(3,7)]
empire_mini
```

```{r ex2-check}
grade_code()
```

<div data-iframe-height></div>