---
output: 
  html_document:
    includes:
      in_header: test1.html
runtime: shiny_prerendered
description: "Vectors & Classes"
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
knitr::opts_chunk$set(echo = FALSE)
tutorial_options(exercise.eval = FALSE)
knitr::opts_chunk$set(exercise.checker = gradethis::grade_learnr)

```

```{css, echo=FALSE}
p {
  font-size: 16.5px;
  font-family: "Merriweather", sans-serif;
}

h5 {
  font-size: 16.5px;
  font-family: "Lato", sans-serif;
}

```

```{r prepare-sat, warning=FALSE, message=FALSE}
library(psych)
sat.act <- sat.act[1:100,]
age <- sat.act$age
act <- sat.act$ACT
satV <- sat.act$SATV
satQ <- sat.act$SATQ
rm(sat.act)
```

##### 1. Create a vector that combines the verbal and quantitative SAT scores to get the students' overall score.
Call this variable `satTotal`. Store it as a new vector *and* print it out

```{r total, exercise = TRUE, exercise.setup = "prepare-sat"}

```

```{r total-solution}
satTotal <- satV + satQ
satTotal
```

```{r total-check}
grade_code()
```

##### 2. Scale the SAT scores so that they are on the same scale as the ACT scores.
A perfect SAT score is 1600 and a perfect ACT score is 36. So let's use a scaling factor of **.0225** (.0225 x 1600 = 36). Call this new variable `scaledSat` and print it out. 

```{r scale, exercise = TRUE, exercise.setup = "prepare-sat"}

```

```{r scale-solution}
scaledSat <- satTotal * .0225
scaledSat
```

```{r scale-check}
grade_code()
```

##### 3. Finally, get the average of the scaled SAT and the ACT scores.
Call it `avgTestScores` and print it out.

```{r avg, exercise = TRUE, exercise.setup = "prepare-sat"}

```

<div id="avg-hint">
<font size="-1.5">
**Hint:** Order of operations matters!
</font>
</div>

```{r avg-solution}
avgTestScores <- (scaledSat + act) / 2
avgTestScores
```

```{r avg-check}
grade_code()
```

<div data-iframe-height></div>